### 2020-03-04 doc/icfp20/harmony.tex
add harmonization figure
harmonization section complete except for diagram

\begin{alltt}
previousTriads : Triad → List Triad
previousTriads I   = V :: IV :: VII :: []
previousTriads II  = VI :: IV :: []
-- other cases omitted for space
\end{alltt}

@@

As Piston does we require the harmonizing triad to include the melody
note. We use a function \texttt{harmonizations} to generate a list of
all candidate harmonizations for a given melody. For space
considerations we refer the reader to the supplement
\texttt{Harmony.agda} for its definition. Here again we encounter difficulties
with equality and membership. We use a bit vector to represent the
set of scale degrees in a triad, where each scale degree is mapped to
an element of \texttt{Fin 7}.

We next restrict to progressions ending in a half cadence (V) to match
Piston's example. This results in 25 candidate progressions.

See Figure~\ref{fig:harmonizationMT}, which is currently just a copy of
the other figure, but included here now for space.

@@

TODO: More comparison.

>>>>

\begin{alltt}
previousTriads : Triad \(\rightarrow\) List Triad
previousTriads I   = V :: IV :: VII :: []
previousTriads II  = VI :: IV :: []
-- other cases omitted for space
\end{alltt}

@@

As Piston does we require the harmonizing triad to include the melody
note. We use a function \texttt{harmonizations} to generate a list of
all candidate harmonizations for a given melody. For space
considerations we refer the reader to the supplement
\texttt{Harmony.agda} for its definition. Here again we encounter difficulties
with equality and membership. We use a bit vector to represent the
set of scale degrees in a triad, where each scale degree is mapped to
an element of \texttt{Fin 7}. However we are able to make use of
dependent types in the form of vectors to ensure the length of each
harmonization matches the melody, and continue to use vectors in the
following functions where appropriate.

We next restrict to progressions ending in a half cadence (V) to match
Piston's example (\texttt{filter halfCadence}). This results in 25
candidate progressions. For each pitch and triad pair we construct a
\texttt{harmonizingChord} in root position with the root doubled. The
function \texttt{voiceChord} spaces the notes nicely. All of this work
ins done in the function \texttt{voicedHarmonizations}.

\begin{alltt}
voicedHarmonizations : \{n : N\} \(\rightarrow\) Vec Pitch n \(\rightarrow\) List (Vec (Vec Pitch 4) n)
voicedHarmonizations \{n\} ps =
  let ds = map pitchToDegreeCMajor ps
      hs : List (Vec Triad n)
      hs = filter halfCadence (harmonizations ds)
      in map (\(\lambda\) ts \(\rightarrow\) map (\(\lambda\) pt \(\rightarrow\)
             \(\text{proj}_1\) pt :: harmonizingChord (\(\text{proj}_1\) pt) (\(\text{proj}_2\) pt)) (zip ps ts)) hs
\end{alltt}

To determine the ``best'' of these harmonizations, we now make use of
\texttt{motionCheck} from the counterpoint work. We compare all six
pairs of melodies, count the number of motion errors present, and pick
the harmonization which minimizes these flaws. The functon to
determine all errors is straightfoward.

\begin{alltt}
motionErrors : \{n : N\} \(\rightarrow\) Vec (Vec Pitch 4) n \(\rightarrow\) List MotionError
motionErrors xs =
  let ss = map (head) xs
      as = map (head \(\circ\) tail) xs
      ts = map (head \(\circ\) tail \(\circ\) tail) xs
      bs = map (head \(\circ\) tail \(\circ\) tail \(\circ\) tail) xs

      sas = map pitchPairToPitchInterval (toList (zip as ss))
      sts = map pitchPairToPitchInterval (toList (zip ts ss))
      sbs = map pitchPairToPitchInterval (toList (zip bs ss))
      ats = map pitchPairToPitchInterval (toList (zip ts as))
      abs = map pitchPairToPitchInterval (toList (zip bs as))
      tbs = map pitchPairToPitchInterval (toList (zip bs ts))
  in concatMap checkMotion (sas :: sts :: sbs :: ats :: abs :: tbs :: [])
\end{alltt}

The harmonization produced is shown in Figure~\ref{fig:harmonizationMT}.

@@

Our harmonization follows Piston's rules more closely and has arguably
better spacing of voices; readers can decide for themselves which is
more pleasing.
